Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-16 paper/paper.tex
wordings

The first set of benchmarks uses the discrete plant of a cruise control
model for the car accounting for rolling friction, aerodynamic drag, and
gravitational disturbance force~\cite{Astrom08} as follows:
%
\begin{equation}
\label{cruise-control-c1}
G_1(z)=\frac{0.0264}{z-0.998} \nonumber
\end{equation}

@@

A third set of benchmarks that consists of a physical plant for satellite
applications is considered~\cite{Franklin15}, in order to evaluate the full
capabilities of the present approach.  In particular, satellites often
require attitude (pose) control for proper orientation of antennas and
sensors w.r.t.~earth.  The satellite attitude control is typically used for
three-axis attitude tracking, but here we consider one axis at a time.  The
motion equation for the one-axis system, disregarding disturbance torques,
is given by
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C}, 
\end{equation}
%
\noindent where $I$ is the inertia moment of the satellite about its mass
center, $\tau_{C}$ is the control torque applied by thrusters, and $\theta$
is the controlled attitude angle.  Normalizing Eq.~\eqref{eq:satelliteode}
by defining the control signal $u=\frac{\tau_{C}}{I}$ and taking the Laplace
transform, the following $s$-domain transfer function $G(s)$ is obtained
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}

\noindent using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
the following $z$-domain model is obtained
%
\begin{equation}
G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
\end{equation}

@@

The fourth (and last) set of benchmarks considers the following description
for the plant $G_{4}(s)$, which is typically used for evaluating stability
margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}
%
\begin{equation}
\label{exampleA}
G_{4}(s)=\frac{s-1}{s^{2}-s-2},
\end{equation}
%
\noindent where $G_{4}(z)$ is obtained using the ZOH discretization defined
in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
and $0.03$ seconds), respectively, as follows:
%
\begin{equation}
\label{exampleA-sampletime1}
G_{4a}(z)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
\end{equation}
%
%
\begin{equation}
\label{exampleA-sampletime2}
G_{4b}(z)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
\end{equation}
%
%
\begin{equation}
\label{exampleA-sampletime3}
G_{4c}(z)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
\end{equation}

@@

\item RQ1 \textbf{(performance)} does the CEGIS approach provide a feasible
solution in reasonable time considering robust stability of FWL digital
controllers?

@@

For the majority of our benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine %inductive back-end 
is able to find a stable solution in less than five minutes.  This is possible if the
inductive solutions need to be refined with few counterexamples and
fixed-point precision increases.  However, two benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$
in Table~\ref{tab:results}).  In these cases, the one-stage engine 
%interval arithmetic back-end 
is able to complement the two-stage approach and synthesize a solution
instead, albeit with significantly larger runtimes.  This performance
difference is due to the fact that the one-stage verification engine does
not take advantage of the inductive conjecture inherent to CEGIS, but
instead fully explores the counterexample space.  The result is a
performance difference of at least two orders of magnitude in our
experiments, leading to the one-stage engine timing out on the majority of
our benchmarks.  Table~\ref{tab:results} only lists the faster of the two
verification engines for each benchmark, which in $12$ out of $15$
benchmarks is the two-stage one.

@@

The median runtime for our benchmark set is $197$\,s, implying that \tool
can synthesize half of the controllers in less than $5$ minutes.  Overall,
the average synthesis time amounts to approximately $30$ minutes.  With
respect to RQ1 we consider these times short enough to be of practical use
to control engineers.  We further conclude that the approach
using a two-stage verification engine is able to synthesize stable
controllers in $12$ out of the $15$ benchmarks, and can be complemented
using the one-stage engine for $2$ additional benchmarks, where the
inductive conjectures fail.  Both verification engines together enabled
controller synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining
benchmark our approach failed to synthesize a stable controller in the
requested time limits.  This can be addressed by either increasing the fixed
point word widths considered or using floating point arithmetic instead. 
The synthesized controllers were confirmed to be stable outside of our
model representation using MATLAB, positively answering RQ2.
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

>>>>

The first set of benchmarks uses the discrete plant of a cruise control
model for a car, and accounts for rolling friction, aerodynamic drag, and
the gravitational disturbance force~\cite{Astrom08}. The plant model is
given as follows:
%
\begin{equation}
\label{cruise-control-c1}
G_1(z)=\frac{0.0264}{z-0.998} \nonumber
\end{equation}

@@

A third set of benchmarks uses a physical plant for satellite
applications~\cite{Franklin15}.  Satellites often require attitude (pose)
control for proper orientation of antennas and sensors w.r.t.~earth.  The
satellite attitude control is typically used for three-axis attitude
tracking, but here we consider only one axis at a time.  The motion equation
for the one-axis system, disregarding disturbance torques, is given by
%
\begin{equation}
\label{eq:satelliteode}
I\cdot \ddot{\theta} = \tau_{C}, 
\end{equation}
%
\noindent where $I$ is the inertia moment of the satellite about its mass
center, $\tau_{C}$ is the control torque applied by the thrusters, and
$\theta$ is the controlled attitude angle.  Normalizing
Eq.~\eqref{eq:satelliteode} by defining the control signal
$u=\frac{\tau_{C}}{I}$ and taking the Laplace transform, the following
$s$-domain transfer function $G(s)$ is obtained:
%
\begin{equation}
\label{eq:satellitetf}
G_{3}(s)=\frac{\theta(s)}{u(s)}=\frac{1}{s^2},
\end{equation}
%
\noindent Using the ZOH discretization defined in Eq.~\eqref{eq:pulsetf}, 
we get the following $z$-domain model:
%
\begin{equation}
G_{3}(z)= \frac{T^{2}}{2} \frac{z+1}{(z+1)^{2}}. \nonumber
\end{equation}

@@

The fourth (and last) set of benchmarks considers the following description
for the plant $G_{4}(s)$, which is typically used for evaluating stability
margins~\cite{bhattacharyya97, keel_Bhattacharyya_examples}:
%
\begin{equation}
\label{exampleA}
G_{4}(s)=\frac{s-1}{s^{2}-s-2},
\end{equation}
%
\noindent We can obtain $G_{4}(z)$ using the ZOH discretization defined
in Eq.~\eqref{eq:pulsetf} with three different sample times ($0.1$, $0.05$,
and $0.03$ seconds), respectively, as follows:
%
\begin{equation}
\label{exampleA-sampletime1}
G_{4a}(z)=\frac{0.100342181002722z - 0.110876810062963}{1.0z^{2} - 2.12624017619613z + 1.10517091807565}, \nonumber
\end{equation}
%
%
\begin{equation}
\label{exampleA-sampletime2}
G_{4b}(z)=\frac{0.0500422033454653z - 0.0526068264456340}{1.0^{2} - 2.05640034257636z + 1.05127109637602}, \nonumber
\end{equation}
%
%
\begin{equation}
\label{exampleA-sampletime3}
G_{4c}(z)=\frac{0.0300090687252212z - 0.0309228417953966}{1.0^{2} - 2.03228208009387z + 1.03045453395352}. \nonumber
\end{equation}

@@

\item RQ1 \textbf{(performance)} does the CEGIS approach generate a 
FWL digital controller in a reasonable amount of time?

@@

For the majority of our benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine %inductive back-end 
is able to find a stable solution in less than five minutes.  This is possible if the
inductive solutions need to be refined with few counterexamples and
increases of the fixed-point precision.  However, two benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$
in Table~\ref{tab:results}).  In these cases, the one-stage engine 
%interval arithmetic back-end 
is able to complement the two-stage approach and synthesize a solution
instead, albeit with significantly larger runtimes.  This performance
difference is due to the fact that the one-stage verification engine does
not take advantage of the inductive conjecture inherent to CEGIS, but
instead fully explores the counterexample space.  The result is a
performance difference of at least two orders of magnitude in our
experiments, leading to the one-stage engine timing out on the majority of
our benchmarks.  Table~\ref{tab:results} only lists the faster of the two
verification engines for each benchmark, which in $12$ out of $15$
benchmarks is the two-stage one.

@@

The median runtime for our benchmark set is $197$\,s, implying that \tool
can synthesize half of the controllers in less than $5$ minutes.  Overall,
the average synthesis time amounts to approximately $30$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $12$ out of the $15$ benchmarks, and can be complemented using the
one-stage engine for two additional benchmarks, where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $14$ out of $15$ benchmarks.  For the one remaining benchmark
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing the fixed-point word
widths considered or using floating-point arithmetic instead.  The
synthesized controllers were confirmed to be stable outside of our model
representation using MATLAB, positively answering RQ2.  A~link to the full
experimental environment, including scripts to reproduce the results, all
benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
